\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A Guide for International Students

### 2023-10-15 demystify.tex
Updates from Overleaf

\renewcommand{\figurename}{Fig.}
\renewcommand{\tablename}{Tab.}
\def\Section{\S}
\newcommand{\mycomment}[3][\color{blue}]{{#1{{#2}: {#3}}}}
\newcommand{\tvn}[1]{\mycomment{TVN}{#1}}{}
\newcommand{\didi}[1]{\mycomment{Didier}{#1}}{}
\newcommand{\tl}[1]{\mycomment{ThanhLe}{#1}}{}
\newcommand{\red}[1]{{\color{red}{#1}}}

@@

\begin{commentbox}[Xiaokuan]
Chinese students often only look at USNews rankings when selecting their Ph.D. universities (I did that, too, when I was applying for Ph.D. positions).
Now that I am a professor, I find it to be the least promising way.
%
The reason is that USNews does not provide a good metric for evaluating the quality of the Ph.D. program.
%
If you want to do great research, CSRankings is the best way to find good and active professors (which did not exist when I was applying),
since it solely focuses on publications at top-tier CS conferences.
%
Also, 
I think Ph.D. is not only about research; 
you need to also consider your daily life there, since you will (probably) stay for at least five years.
%
You might regret it if you did not consider this seriously before applying.
%
Whether your research interest matches that of your advisor is also important;
if there is a mismatch,
either you or your advisor has to make compromises,
which often leads to disagreements or conflicts.

\end{commentbox}

@@

% \subsubsection{Strong Faculty vs High-ranked School}
% \begin{commentbox}[Thanh]
% When considering PhD programs, we often wonder if we should prioritize a high-ranking university or a professor with a strong reputation? Of course, both are great, but it is hard to achieve both.  I believe receiving some guidance from you  would be incredibly valuable.
% \end{commentbox}

@@

>>>>

\renewcommand{\figurename}{Fig.}
\renewcommand{\tablename}{Tab.}
\def\Section{\S}
\newcommand{\mycomment}[3][\color{blue}]{{#1{{#2}: {#3}}}}
\newcommand{\tvn}[1]{\mycomment{TVN}{#1}}{}
\newcommand{\didi}[1]{\mycomment{Didier}{#1}}{}
\newcommand{\tl}[1]{\mycomment{ThanhLe}{#1}}{}
\newcommand{\red}[1]{{\color{red}{#1}}}
\newcommand{\xz}[1]{\mycomment{Xiaokuan}{[#1]}}{}

@@

\begin{commentbox}[Xiaokuan]
Chinese students often only look at USNews rankings when selecting their Ph.D. universities (I did that, too, when I was applying for Ph.D. positions).
Now that I am a professor, I find it to be the least promising way.
%
The reason is that USNews does not provide a good metric for evaluating the quality of the Ph.D. program.
%
If you want to do great research, CSRankings is the best way to find good and active professors (which did not exist when I was applying),
since it solely focuses on publications at top-tier CS conferences.
%
Also, 
I think Ph.D. is not only about research; 
you need to also consider your daily life there, since you will (probably) stay for at least five years.
%
You might regret it if you did not consider this seriously before applying.
%
\end{commentbox}

@@

\begin{commentbox}[Xiaokuan]
Whether the student's research interest matches that of the advisor is very important;
if there is a mismatch,
either the student or the advisor has to make compromises,
which often leads to disagreements or conflicts. 
IMO, the advisor should be the one who {\it guides}  students to do research while allowing students to pursue their own interest,
instead of {\it dictating} their research.

\end{commentbox}
% \subsubsection{Strong Faculty vs High-ranked School}
% \begin{commentbox}[Thanh]
% When considering PhD programs, we often wonder if we should prioritize a high-ranking university or a professor with a strong reputation? Of course, both are great, but it is hard to achieve both.  I believe receiving some guidance from you  would be incredibly valuable.
% \end{commentbox}

@@

\xz{Applying for Ph.D. and contacting a potential Ph.D. advisor is a classic {\bf `why me, why you'} problem, 
similar to looking for a job in a company.
On a high level,
you need to show that you have done your {\it homework}
regarding the professor and the university,
and clearly explain:
1) why do you think you are a good fit in professor A's group?
2) why do you want to be advised by professor A, not B? 
3) why do you want to apply for university X, not Y?
If you don't want to spend time to do your homework,
the chance of getting a reply is close to zero.
}
